\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-02-28 paper.tex
Save a bit of space by removing/cropping some figures

\end{pythoncode}
    \caption{Example of a simple yet complete \uwds filter, written in Python:
    the client connects to the \uwds network, blocks until the world {\tt
    example\_in} changes, and only propagate nodes that match the condition to
    the world {\tt example\_out}.}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{tools}
    \caption{Screenshots of the timeline (top) and network (bottom)
    introspection tools. Worlds are represented as boxes; clients as ellipses.}
    \label{fig|explorer}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{spatialrelations}
    \caption{The {\tt spatial\_relations} client computes perspective-aware
    spatial relations between objects and agents: \emph{allo-centric} relations (like
    {\tt is in} or {\tt is on}) are independent of the viewpoint, while
    \emph{ego-centric} relations ({\tt in front of}, {\tt left of}) depend on
    the viewer perspective.}
    \label{fig|spatialrelations}
\end{figure}

\uwds provides an exemplary client ({\tt spatial\_relations}) to compute both
allo-centric and ego-centric (\ie viewer-dependent) spatial relations
between objects (Figure~\ref{fig|spatialrelations}).
Other libraries, like QSRLib~\cite{gatsoulis2016qsrlib}, that implement
computational models of Qualitative Spatial Relations could be trivially
combined with \uwds to provide more advanced geometric analysis.

>>>>

\end{pythoncode}
    \caption{Example of a simple yet complete \uwds filter, written in Python:
    the client connects to the \uwds network, blocks until the world {\tt
    world1} changes, and only propagate nodes that match the condition to
    the world {\tt world2}.}

@@

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{tools}
    \caption{Screenshot of the network topology introspection tool. Worlds are represented as boxes; clients as ellipses.}
    \label{fig|explorer}
\end{figure}

@@

%\begin{figure}
%    \centering
%    \includegraphics[width=\linewidth]{spatialrelations}
%    \caption{The {\tt spatial\_relations} client computes perspective-aware
%    spatial relations between objects and agents: \emph{allo-centric} relations  are independent of the viewpoint, while
%    \emph{ego-centric} relations ({\tt in front of}, {\tt left of}) depend on
%    the viewer perspective.}
%    \label{fig|spatialrelations}
%\end{figure}

\uwds provides an exemplary client ({\tt spatial\_relations}) to compute both
allo-centric (independent of the viewpoint like {\tt isIn} or {\tt isOn}) and
ego-centric (\ie viewer-dependent, like {\tt inFrontOf} or {\tt leftOf}) spatial relations
between objects.
%(Figure~\ref{fig|spatialrelations}).
Other libraries, like QSRLib~\cite{gatsoulis2016qsrlib}, that implement
computational models of Qualitative Spatial Relations could be trivially
combined with \uwds to provide more advanced geometric analysis.
